%!TEX root = ../TTK4550-MHT.tex
\section{Closing remarks}
\subsection{Conclusion}
This report has shown that off-the-shelf \gls{ilp} \glspl{solver}, both free and commercial, are capable solving the data association problem in a \gls{tomht}. It has also provided evidence that the \gls{tracking} performance does benefit very little from more than $N=3$ scan history in moderate manoeuvring scenarios when \gls{Pd} $> 70\%$, even with severe amounts of \gls{clutter}.

Through simulations on a single-core implementation of a \gls{tomht} in \gls{python}, it have also shown the feasibility for real-time applications with five closely spaced targets with $N=5$ in a heavy clutter scenario ($\lambda_\phi = 1 \cdot 10^{-3}$), and $N=6$ for a moderate clutter scenario ($\lambda_\phi = 5 \cdot 10 ^{-4}$). Further, this report has  outlined the possibilities for significant rune-time improvements through the use of multi-core \glspl{cpu} and \glspl{gpu}.

\subsection{Future work}
One area where there might be substantial benefits, is in more complex \gls{pruning} and merging of hypotheses. By nature, many hypotheses will have very similar paths (see Figure \ref{fig:track_hypotheses_example}) and could therefore be candidates for being merged to one. The danger with this is that the assignment problem could be rendered infeasible and crash the algorithm. A novel approach could be to formulate the pruning as an optimization problem. With this approach it is possible to also remove hypotheses with a low score, subject to the problem still being feasible.

In the maritime context, it could also be very beneficial to use the maritime \gls{ais} to aid the \gls{tracking}. There are different approaches to include this extra set of data, all with their pros and cons. One option could be to use the \gls{ais} track to weight the measurements from the radar; this way the measurement that are more likely to originate from a target is given a higher score. Another possibility is to do track-to-track fusion / filtering, where the best or N-best tracks from the radar are filtered with the tracks from the AIS system. Track-to-track fusion can also be handled within the ILP framework, see \cite{Coraluppi2000}.

%Another improvement that would benefit the run time requirement is to parallelize  the algorithm. Since many of the operations in the algorithm are independent, they are excellent candidates for running in parallel. Today CPU's can be delivered with as many as 24 cores per die, and with hyper threading they can process op to 48 threads. With server grade motherboards capable of one to four CPU's, there is potential to run almost 200 threads if necessary. This would however be a pure brute force approach, which would push the boundary of how many targets the system would be able to track simultaneously, but not the run time as a function of the problem size.

A final but very important piece, that is required for the system to be complete, is track initialization. As with \gls{ais} assisted \gls{tracking}, there are plenty of ways to tackle this challenge, some of them mentioned in section \ref{subsec:tomht}. %One alternative, and probably the most common for \gls{tomht} is to run a separate system besides the \gls{tracking} loop to initiate targets. This system can be based on recursive RANSAC, \gls{pdaf}-based techniques, etc., with a selection criterion for declaring a target born. The most common is a N out of M threshold, where N and M may be 4 and 6 respectively. These separate initialization trackers can run on all measurements, or maybe preferably on the non-associated measurements from the primary system.