%!TEX root = ../TTK4550-MHT.tex
\section{Discussion}
\label{sec:discussion}
The field of tracking and data association has been dominated by firstly military applications, and by secondly civil aviation control. Both of which are areas with hight performance demands and large development contracts \cite{Blackman2004}. Although much work is published on this topic, few comparisons have been made between actual implementations of different trackers and filters. This may to some extent be due to the nature of business secrets and military classifications to hide the intricate details that goes into an actual implementation and optimization of any tracking system. It is also, on a slightly more speculative note, due to disagreements about what kind of performance measures one should use. 

One of the main objectives for this work was to examine the feasibility of using off-the-shelf solvers to solve the assignment problem in a \gls{mht} system. This report have shown that all of the tested solvers ere capable of solving the assignment problem. It has also shown that there are some drawbacks with using off-the-shelf solvers. The largest ones beeing that the assignment problem must be written to a file that the solver can interpret. This is a major drawback with the chosen approach, but can be partially compensated for with fast \gls{ssd} in stead of traditional rotating hard drives. Another major drawback is the need for explicit enumeration of all hypotheses in the \gls{ilp} formulation, which is costly and in many situations unnecessary. This could possibly be addressed by column generating optimization methods \cite{Barnhart1998}, starting with a feasible set of columns and adding more and more columns (constraints) until it reaches the optimal assignment. Intuitively this makes sense, as most of the constraints will never be active, and therefore not needed for finding the optimal solution. This would, however, make the optimization a lot more tailor-made to this application, and render the usage of off-the-shelf solvers impossible.